---
title: "10-import"
output: html_notebook
---
I'd like this to replace my score for the coding section of assignment 3.

## Problem 

This dataset contains observations of shootings in the US for 2016. It contains values for the number of people killed and wounded per shooting. It also contains data on the date and location of the shooting. 

I want to know what time of year has the highest amount of mass shootings. It is believed that the summer is when shootings are most likely to occur. I also want to see which states and cities have the highest number of people injured (killed and wounded) from mass shootings. 
## Needed libraries

```{r import_libraries}
library(tidyverse)
library(readr)
library(assertr)
library(lubridate)
library(janitor)
```

## Import Data and clean names

```{r import_data}
Mass_Shooting_Data_2016_2016 <- read_csv("Mass Shooting Data 2016 - 2016.csv") %>%
  clean_names()
```

## Check columns for NA values

We want to check all of the columns to if there are any NA values present. 

```{r col_na}
for(col_name in names(Mass_Shooting_Data_2016_2016)) {
  Mass_Shooting_Data_2016_2016 %>% 
    assert(not_na, col_name)
}
```

Using the assert are command not_na we find that there are no NAs in any of the columns. 

## Check killed column for negative values

We want to make sure there are no negative values in the killed column of this data set since it is not possible to kill negative people. 
```{r neg_killed}
Mass_Shooting_Data_2016_2016 <- read_csv("Mass Shooting Data 2016 - 2016.csv") %>%
  assert(within_bounds(0,Inf), killed)
```
We checked within the bounds from 0 to infinity and it showed us that all of the values in the killed column of the data were either 0 or positive. 
## Check wounded column for negative values

We want to do the same assertr command we used for the killing column on the wounded column.
```{r neg_wounded}
Mass_Shooting_Data_2016_2016 <- read_csv("Mass Shooting Data 2016 - 2016.csv") %>%
  assert(within_bounds(0,Inf), wounded)
```
Using the same bounds we find that all values in the wounded column are either 0 or positive. 

## Editing variable type for date

The date variable is currently a character, but we want to make it a date. We also want it to be formatted in year-month-day format. 

```{r date_format}
Mass_Shooting_Data_2016_2016 <- Mass_Shooting_Data_2016_2016 %>%
  mutate(date = mdy(date))
```

 