---
title: "assign4"
output: html_notebook
---

```{r}
library(tidyverse)
library(lubridate)
library(RVerbalExpressions)
```

For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 

```{r}
first_month <- (floor_date(unit = "year", today()) + month(0:11))
```


Write a function that given your birthday (as a date), returns how old you are in years.
```{r}
age <- function(date) {
 time_length(difftime(today(), ymd(date)), "years")
}

age(19951128)
```


Write a function that given your birthday, returns the day of the week you were born on. 

```{r}
day_of_week <- function(day){
  wday(day, label = TRUE)
}

day_of_week(ymd(19951128))
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)

```{r}
stringr::words
words

## Regular Expression

str_view(words, ".{7,}", match = TRUE)

## Verbal Expression

seven_letters <- rx() %>%
  rx_word_char() %>%
  rx_repeat_previous(7) %>%
  rx_anything() %>%
  print()

str_view(words, seven_letters, match = TRUE)
```


## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)

```{r}
str_subset(words, "^[^aeiou]+$")

consonants <- rx() %>%
  rx_start_of_line() %>%
  rx_anything_but("aeiou") %>%
  rx_end_of_line()
  
str_subset(words, consonants)
```


Empirically verify the rule “i before e except after c”.

```{r}
x <- str_subset(words, "([^c]ie|cei)")
length(x)

after_c <- rx() %>%
  rx_find("c") %>%
  rx_anything_but("ie") %>%
  rx_find("ei")

i_before_e <- rx() %>%
  rx_something_but("c") %>%
  rx_find("ie")
  
  
after_c_vec <- str_subset(words, after_c)
i_before_e_vec <- str_subset(words, i_before_e)
length(after_c_vec) + length(i_before_e_vec)
```


Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.

```{r}
y <- c("123-456-7890", "123.456.7890", "1234567890", "(123)456-7890", "1234", "12-345-9")

## Regular Expression

str_view(y, "([0-9]{3}-[0-9]{3}-[0-9]{4}|[0-9]{3}.[0-9]{3}.[0-9]{4}|[0-9]{10}|([0-9]{3})[0-9]{3}-[0-9]{4})")

## Verbal Expression

telrx <- rx() %>%
  rx_start_of_line() %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_any_of("-.") %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_any_of("-.") %>%
  rx_digit() %>%
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>%
  print() %>%
  grepl(c("217-377-2867", "217.377.2867", "EM7.377.2867")) %>%
  print()
```


# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

